Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-04-21 reports/manuscript/supplemental_changes.tex
Add harmonization info and plots

@@

>>>>

\usepackage[commentmarkup=footnote]{changes}

@@

\section{\added{Data harmonization in the HBN dataset}}

\added{\Cref{fig:hbn-site-bp:fa,fig:hbn-site-bp:md} show the bundle profiles for the HBN dataset separated by scanner site: Rutgers Rutgers University Brain Imaging Center (RU) and the CitiGroup Cornell Brain Imaging Center (CBIC). We see strong site differences in both FA and MD profiles. Conversely, \cref{fig:hbn-site-age-dist} shows that the age distributions at each site are similar. ComBat effectively harmonizes the scanner site differences, as shown in \cref{fig:hbn-harmonized-bp:fa,fig:hbn-harmonized-bp:md}.}

\begin{figure}
    \includegraphics[width=0.9\textwidth]{hbn_site_age_distributions.pdf}
    \caption{%
        {%
            \bf Age distributions are similar between the different
            HBN sites.
        }
        \label{fig:hbn-site-age-dist}
    }
\end{figure}

\begin{figure}
    \includegraphics[width=0.9\textwidth]{hbn_site_profiles_fa.pdf}
    \caption{%
        {%
            \bf Fractional anisotropy (FA) bundle profiles
            exhibit strong site differences in the HBN dataset.
        }
        \label{fig:hbn-site-bp:fa}
    }
\end{figure}

\begin{figure}
    \includegraphics[width=0.9\textwidth]{hbn_site_profiles_md.pdf}
    \caption{%
        {%
            \bf Mean diffusivity (MD) bundle profiles
            exhibit strong site differences in the HBN dataset.
        }
        \label{fig:hbn-site-bp:md}
    }
\end{figure}

\begin{figure}
    \includegraphics[width=0.9\textwidth]{hbn_harmonized_profiles_fa.pdf}
    \caption{%
        {%
            \bf Site differences in fractional anisotropy (FA)
            do not survive ComBat harmonization.
        }
        \label{fig:hbn-harmonized-bp:fa}
    }
\end{figure}

\begin{figure}
    \includegraphics[width=0.9\textwidth]{hbn_harmonized_profiles_md.pdf}
    \caption{%
        {%
            \bf Site differences in mean diffusivity (MD)
            do not survive ComBat harmonization.
        }
        \label{fig:hbn-harmonized-bp:md}
    }
\end{figure}

\pagebreak
